\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-18 design.tex
move test diagram

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.8\textwidth]{teststate.png}
	\end{center}
	\caption{The test lifecycle state machine.}
	\label{fig:teststate}
\end{figure}
Landslide knows the state of the test case through a simple state machine, which is updated with information about the number of threads currently on the system, the number of threads on the runqueue, the state of the idle thread (if it exists), and whether or not the shell is waiting for keyboard input.

@@

The states in the test lifecycle, and the rules for transitioning between them, are as follows.
Figure~\ref{fig:teststate} depicts the states and transitions visually.

>>>>

Landslide knows the state of the test case through a simple state machine, which is updated with information about the number of threads currently on the system, the number of threads on the runqueue, the state of the idle thread (if it exists), and whether or not the shell is waiting for keyboard input.

@@

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.8\textwidth]{teststate.png}
	\end{center}
	\caption{The test lifecycle state machine.}
	\label{fig:teststate}
\end{figure}
The states in the test lifecycle, and the rules for transitioning between them, are as follows.
Figure~\ref{fig:teststate} depicts the states and transitions visually.
